\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{titlesec}

% Define colors for code listings
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}

\lstset{style=mystyle}

\title{\Huge Parking-Smart Deployment Guide \\ \Large Vercel Infrastructure Setup}
\author{Technical Infrastructure Team}
\date{\today}

\begin{document}

\maketitle
\tableofcontents
\newpage

\section{Introduction}
This document outlines the professional deployment procedures for the Parking-Smart ecosystem on the Vercel platform. The system is split into two distinct deployments:
\begin{enumerate}
    \item \textbf{Backend API:} Node.js Express server located in the root directory.
    \item \textbf{Frontend Dashboard:} Next.js application located in \texttt{/parking-smart-dashboard}.
\end{enumerate}

\section{Prerequisites}
Before beginning the deployment, ensure the following are available:
\begin{itemize}
    \item A Vercel account (\url{https://vercel.com}).
    \item A managed PostgreSQL database (e.g., Supabase, Neon, or Railway).
    \item Your project repository hosted on GitHub, GitLab, or Bitbucket.
\end{itemize}

\section{External Database Provisioning}
Since the backend is deployed as a set of Serverless Functions on Vercel, it cannot host a local persistent database. You \textbf{must} provision an external PostgreSQL instance.

\subsection{Recommended Providers}
\begin{itemize}
    \item \textbf{Supabase:} Offers a generous free tier and easy-to-use GUI (\url{https://supabase.com}).
    \item \textbf{Neon:} A serverless PostgreSQL built for scale (\url{https://neon.tech}).
    \item \textbf{Railway:} Simple provisioning with a flat-fee or usage-based model (\url{https://railway.app}).
\end{itemize}

\subsection{Connection String Requirements}
Once your database is created, obtain the \textbf{Connection URI}. It typically follows this format:
\begin{center}
    \texttt{postgres://user:password@host:port/dbname?sslmode=require}
\end{center}
\textbf{Important:} Ensure that \texttt{sslmode=require} is enabled, as most managed providers require SSL for secure connections from serverless environments.

\section{Backend Deployment (Root API)}
The backend is a Node.js Express application. Since it resides in the root of the repository, we use a \texttt{vercel.json} configuration to enable Serverless Functions.

\subsection{Vercel Configuration}
Ensure \texttt{vercel.json} exists in the root directory with the following content to enable CORS and Serverless mapping:
\begin{lstlisting}[language=json]
{
  "version": 2,
  "builds": [
    { "src": "src/app.js", "use": "@vercel/node" }
  ],
  "routes": [
    {
      "src": "/(.*)",
      "dest": "src/app.js",
      "headers": {
        "Access-Control-Allow-Origin": "*",
        "Access-Control-Allow-Methods": "GET,OPTIONS,PATCH,DELETE,POST,PUT",
        "Access-Control-Allow-Headers": "X-Requested-With, Content-Type, Authorization"
      }
    }
  ]
}
\end{lstlisting}

\subsection{Vercel Configuration}
While Next.js is zero-config, we include a \texttt{vercel.json} for explicit project association:
\begin{lstlisting}[language=json]
{
  "version": 2,
  "framework": "nextjs"
}
\end{lstlisting}

\subsection{Deployment Steps}
\begin{enumerate}
    \item Log in to the Vercel Dashboard and click \textbf{New Project}.
    \item Import the \texttt{Parking-Smart} repository.
    \item Ensure the \textbf{Root Directory} is set to \texttt{./} (the default).
    \item In the \textbf{Environment Variables} section, add the following:
    \begin{itemize}
        \item \texttt{DATABASE\_URL}: Your PostgreSQL connection string.
        \item \texttt{PORT}: 3000 (Optional, Vercel sets this automatically).
    \end{itemize}
    \item Click \textbf{Deploy}.
\end{enumerate}

\section{Frontend Deployment (Dashboard)}
The dashboard is a Next.js application. Vercel detects this automatically but requires the correct directory setting.

\subsection{Deployment Steps}
\begin{enumerate}
    \item Click \textbf{New Project} in the Vercel Dashboard.
    \item Import the same \texttt{Parking-Smart} repository.
    \item \textbf{CRITICAL:} Set the \textbf{Root Directory} to \texttt{parking-smart-dashboard}.
    \item Vercel will auto-detect the Next.js framework.
    \item In \textbf{Environment Variables}, add:
    \begin{itemize}
        \item \texttt{NEXT\_PUBLIC\_API\_URL}: The URL of your deployed Backend API.
    \end{itemize}
    \item Click \textbf{Deploy}.
\end{enumerate}

\section{Post-Deployment Verification}
Once both services are live:
\begin{itemize}
    \item Verify backend health: Navigate to \texttt{https://your-api-url.vercel.app/health}.
    \item Verify Swagger docs: Navigate to \texttt{https://your-api-url.vercel.app/api-docs}.
    \item Access the Dashboard: Ensure it correctly fetches data from the Backend API URL.
\section{Troubleshooting Vercel Crashes}
If you encounter a \texttt{500: INTERNAL\_SERVER\_ERROR} or \texttt{FUNCTION\_INVOCATION\_FAILED}, check the following:

\begin{itemize}
    \item \textbf{Environment Variables:} Ensure \texttt{DB\_URI} is correctly set in the Vercel Dashboard. The backend cannot start without a valid database connection.
    \item \textbf{Database Accessibility:} Ensure your PostgreSQL provider (e.g., Supabase) allows connections from all IP addresses OR specifically from Vercel's IP range.
    \item \textbf{Serverless Timeouts:} The first run (\texttt{sequelize.sync}) might take longer than the default Vercel timeout. Ensure your database is initialized.
    \item \textbf{Logs:} Use the \textbf{Logs} tab in the Vercel Dashboard to see the exact Node.js stack trace causing the crash.
\end{itemize}

\end{document}
